Lnc34a CAGE

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
grouped identical reads in CAGE figure

---
title: "Lnc34a CAGE"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    code_folding: hide
    theme: flatly
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

@@

gdata <- bind_rows(gdata, pw) %>%
  mutate(gene = readr::parse_factor(gene, levels = c("Primers", "lnc34a", "miR34a asRNA")))

#cage data
url <- fileMap(type = "rds")["suppFigure4a"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

#genes
p1 <- ggplot(data = NULL) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.5, label = fill),
    size = 3,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

@@

#genes
p1 <- ggplot(data = NULL) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.25
  ) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.65, label = fill),
    size = 1.75,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 6),
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

@@

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
g <- resize_heights(g, unit(c(5, 1, 1.5), "null"))
#grid.draw(g)

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
ggsave(
  plot = g,
  filename = path,
  device = cairo_pdf,
  height = 150,
  width = 90,
  units = "mm"
)
```

>>>>

---
title: "Lnc34a CAGE"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: flatly
  pdf_document: default
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

@@

gdata <- bind_rows(gdata, pw) %>%
  mutate(gene = readr::parse_factor(gene, levels = c("miR34a asRNA", "lnc34a", "Primers")))

#cage data
url <- fileMap(type = "rds")["suppFigure4a"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
  select(start, stop, level) %>%
  group_by(start, stop) %>%
  summarize(level = sum(level)) %>%
  ungroup() %>%
  arrange(desc(level)) %>%
  mutate(y = 1:n())

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill, group = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene, group = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.5, label = fill),
    size = 3,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.25
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.55, label = fill),
    size = 1.75,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 6),
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

@@

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
g <- resize_heights(g, unit(c(5, 1, 2), "null"))
#grid.draw(g)

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
ggsave(
  plot = g,
  filename = path,
  device = cairo_pdf,
  height = 100,
  width = 90,
  units = "mm"
)
```
